### 2017-08-11 Paper01_EnthalpyAndCrystallization.tex
Results - intro - updated film thickness and dep rate. Added figures to show new calcs.

From the 35 minute depositions a nominal film thickness of $2.5 \mu m$ was obtained, giving a deposition rate of approximately $1.2 nm/s$. The temperature within the chamber was found to rise $2.9 - 3.5$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}.

>>>>

From the 35 minute depositions a nominal film thickness of $1.64 \pm 0.48 \mu m$ was obtained, giving a deposition rate of approximately $0.81 \pm 0.22 nm/s$, see Figure \ref{fig:Film_Thickness_DepRate}. The temperature within the chamber was found to rise $2.9 - 3.5$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}.

%code to put 2 images side by side in a figure
\begin{figure}[h]
	\centering
	%Image 1
	\begin{subfigure}[htbp]{0.4\textwidth}
		\includegraphics[width=\textwidth]{Film_Thickness.png}
		\caption{}
		\label{fig:Film_Thickness}
	\end{subfigure}
	%Image 2
	\begin{subfigure}[htbp]{0.4\textwidth}
		\includegraphics[width=\textwidth]{Deposition_Rate.png}
		\caption{}
		\label{fig:Deposition_Rate}
	\end{subfigure}
	\caption{(a) Box and whisker plot of the measured film thicknesses from depositions. (b) Box and whisker plot of the calculated deposition rates achieved.}%global caption
	\label{fig:Film_Thickness_DepRate}
\end{figure}
